### 2015-02-27 icfp15-servo/servo.tex
Remove 'and/or'; 'or' is already non-exclusive.
Add a note about cross-language inlining

There are two limitations in the language interoperability that pose challenges for Servo today.
First, Rust cannot currently expose varargs-style functions to C code.
Second, Rust cannot compile against \Cplusplus{} code.
In both cases, Servo uses C wrapper code to call into the code that Rust cannot directly
reach.
While this approach is not a large problem for varargs-style functions, it defeats many of the
places where the \Cplusplus{} code has been crafted to ensure the code is inlined into the caller,
resulting in degraded performance.

@@

As the ``lint'' / ``warning'' terminology suggests, these checks may not catch all possible mistakes. Ad-hoc extensions to a type system cannot easily guarantee soundness. Rather, lint plugins are a lightweight way to catch mistakes deemed particularly common and/or damaging in practice. As plugins are ordinary libraries, members of the Rust community can share lint checks that they have found useful.\footnote{\url{https://github.com/Manishearth/rust-clippy}}

>>>>

There are two limitations in the language interoperability that pose challenges for Servo today.
First, Rust cannot currently expose varargs-style functions to C code.
Second, Rust cannot compile against \Cplusplus{} code.
In both cases, Servo uses C wrapper code to call into the code that Rust cannot directly
reach.
While this approach is not a large problem for varargs-style functions, it defeats many of the
places where the \Cplusplus{} code has been crafted to ensure the code is inlined into the caller,
resulting in degraded performance. We intend to fix this through cross-language inlining, taking
advantage of the fact that both \lstinline{rustc} and \lstinline{clang++} can produce output in the
LLVM\footnote{\url{http://llvm.org}} intermediate representation, which is subject to link-time
optimization. We have demonstrated this capability at small scale, but have not yet deployed it
within Servo.

@@

As the ``lint'' / ``warning'' terminology suggests, these checks may not catch all possible mistakes. Ad-hoc extensions to a type system cannot easily guarantee soundness. Rather, lint plugins are a lightweight way to catch mistakes deemed particularly common or damaging in practice. As plugins are ordinary libraries, members of the Rust community can share lint checks that they have found useful.\footnote{\url{https://github.com/Manishearth/rust-clippy}}
